% ./end-matter/vita.tex
% ============================================================================ %
\documentclass[../main.tex]{subfiles}
\begin{document}%
% ============================================================================ %
    \chapter*{Vita}%
    \addcontentsline{toc}{chapter}{Vita}%
    % ======================================================================== %
    Elan Hunter Herrera is an engineer from Dallas, Texas.
    In 2007 he earned his high school diploma from Edward S. Marcus High School in Flower Mound, TX. 
    While in high school he also worked with the robot team and was employed at Fry’s Electronics as a Mobile Electronics Certified Technician. 
    He attended \gls{university-texas} where he studied Mechanical Engineering. 
    During his studies, he trained as a Reactor Operator at the department managed \glstext{triga} Mk II nuclear research reactor.
    He completed his Bachelors of Science degree in 2013 with a specialization in Nuclear Engineering. 
    % ======================================================================== %
    \Xfigurefile{author-portrait}%
    % ======================================================================== %
    \FloatBarrier%
    % ======================================================================== %
    Later, he relocated to Knoxville, Tennessee, in pursuit of a Ph.D. in Nuclear Engineering. 
    There, he studied under Dr. Eric Lukosi, researching a novel semiconducting neutron detector, \gls{lise} \cite{Lukosi_2014,Stowe_2014,Hamm_2015,Lukosi_2016a,Herrera_2016,Lukosi_2017,Herrera_2018,Hamm_2018} obtaining his Masters of Science degree in 2015. 
    He went on to write this dissertation, using \gls{latex} \cite{book:Mittelbach_2004}, in completion of the degree of Doctor of Philosophy in Nuclear Engineering.
% ============================================================================ %
\end{document}%