% ./front-matter/acknowledgments.tex
% ============================================================================ %
\documentclass[../main.tex]{subfiles}
\begin{document}%
% ============================================================================ %
    \chapter*{Acknowledgments}%
    \begin{flushleft}%
    % ======================================================================== %
        \def\tmp{1.0ex}%
        % ==================================================================== %
        \textbf{To my family:}\\%
        % ==================================================================== %
        Thank you to my grandparents, \emph{Lilia and Faustino Herrera}, for pushing me to achieve my goals and more. 
        You have been my unfaltering support and inspiration through the entirety of my academic career.
        I love you both very much.
        Thank you to my father, \emph{Eduardo Herrera} for supporting and encouraging my academic pursuits.
        Thank you to my aunt and uncle, \emph{Jaime and Pamela Herrera}, for opening your home and supporting my completion of graduate school.\\%
        % ==================================================================== %
        \vspace{\tmp}%
        \textbf{To my colleagues:}\\%
        % ==================================================================== %
        Thank you to my close friend \emph{Jae-Ho Song}.
        You have been an unconditional ally in the pursuit of scientific and engineering excellence, providing invaluable collaboration on numerous projects.\\%
        % ==================================================================== %
        Thank you to my colleagues at the Univeristy of Tennessee:\ %
        \emph{%
            Dustin Giltnane,
            Dr. Daniel S. Hamm,
            Robert W. Milburn,
            C. Ryan Priest,
            M. Dylan Richardson,
            Mikah R. Rust,
            and
            Dr. Thomas G. Wulz%
        }.\\%
        % ==================================================================== %
        Thank you to my colleagues at The Univeristy of Texas at Austin:\ %
        \emph{%
            Austin Davis,            
            Hunter Fuentes,
            Jason Guidry,
            Jacob Navar,
            Johnathan Sims,
            Sigmund S{\o}gnesand,
            and
            Nick Wynne
        }.\\%
        % ==================================================================== %
        Thank you to all the collaborators on the LISe Project from Fisk University, Oak Ridge National Lab, University of Tennessee, Vanderbilt University, and Y-12 National Security Complex.\\%
        % ==================================================================== %
        \vspace{\tmp}%
        \textbf{To the McNair Scholars Program:}\\%
        % ==================================================================== %
        Thank you to all the faculty and staff from The University of Texas at Austin and especially \emph{Dr. James Brown} for your guidance and support.\\%
        \vspace{\tmp}%
        % ==================================================================== %
        \vspace{\tmp}%
        \textbf{To my academic mentors:}\\%
        % ==================================================================== %
        Thank you to my Senior Reactor Operator and Supervisor, Michael Krause, for teaching me to operate the TRIGA nuclear reactor and instilling an appreciation for the nuclear security culture.\\%
        Thank you to my undergraduate faculty mentor, \emph{Dr. Sheldon Landsberger}, for overseeing my undergraduate research and senior design project, introducing me to the field of nuclear engineering.\\%
        Thank you to my graduate advisor, \emph{Dr. Eric D. Lukosi}, for allowing me to work on the LISe Project.\\%
        % ==================================================================== %
        \vspace{\fill}%
        % ==================================================================== %
        \ResearchFundingBlock{%
            This work is supported through subcontract number 4300090406 from CNS Y-12 National Security Complex and this material is based upon work supported under a Department of Energy Nuclear Energy University Programs Graduate Fellowship.
            A portion of this research at ORNL’s High Flux Isotope Reactor was sponsored by the Scientific User Facilities Division, Office of Basic Energy Sciences, U.S. Department of Energy.
        }%    
    % ======================================================================== %
    \end{flushleft}%
    % ======================================================================== %
    \newpage%
    % ======================================================================== %
    \begin{spacing}{1.5}%
        \begin{center}%
            \textit{A special thank you to all the members of my Doctoral Committee, for your advisement and support.}\\%
            \Xfigurefile{committee-mosaic}%    
        \end{center}%
    \end{spacing}%
% ============================================================================ %
\end{document}%